---
title: 'MSBR 70200 In-Class Exercise: Inventory Management for HP Printers'
author: "Chamroeun Chhay"
date: "9/10/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

<br>

##### HP sells its versatile PSC2310 Printer in both Switzerland and Germany. 
Due to some local differences (i.e., ever so slightly different power plugs, warranty papers, language of user manuals etc.), its central warehouse in Schwabia stocks different SKUs for each country. *That is, printers for Switzerland cannot be sent to Germany and vice versa.*
Monthly demands in Germany (X) and Switzerland (Y) are normally distributed with:

<br>

|        | Germany (X) | Switzerland (Y) |
|:-------|:-------:|:------------------:|
|Mean | 4200 | 420 |
|Std. Deviation | 2200  | 200 |

This information is stored in the following variables.

```{r}
# Germany (X)
mu_X <- 4200
sd_X <- 2200

# Switzerland (Y)
mu_Y <- 420
sd_Y <- 200
```

Remind that R provides the following functions for a normal distribution.

-	`dnorm`: probability density function (PDF)
-	`pnorm`: cumulative distribution function (CDF)
-	`qnorm`: quantile function
-	`rnorm`: random normal number generating function

<br>

* * *



#### 1. What is the probability that the demand in Switzerland exceeds 600 units in a month?

 - Mathematical expression: $P(Y>600)$
 

 - R code
    ```{r}
    pnorm(600, mean = mu_Y, sd = sd_Y, lower.tail = FALSE)
    
    # or
    1 - pnorm(600, mean = mu_Y, sd = sd_Y, lower.tail = TRUE)
    ```
 
 - If we carry 600 printers for Switzerland, we can satisfy the demand with the probability of `r pnorm(600, mean = mu_Y, sd = sd_Y, lower.tail = TRUE)`. However, we will be out of stock with the probability of `r pnorm(600, mean = mu_Y, sd = sd_Y, lower.tail = FALSE)`.
 
<br>
<br>
<br>

#### 2. How much should HP stock each SKU for Germany and Switzerland, respectively, for one omonth if 98% of **all** demand should be satisfied? What is the total required stock level? (Assume that two demands are independent.) 

 - Mathematical expression:
 - R code
    ```{r}
    # required stock level for Germany (X)
qnorm(.98, mu_X, sd_X)
pnorm(8718.248, mu_X, sd_X, T)
    
    # required stock level for Switzerland (Y)
qnorm(.98, mu_Y, sd_Y)
pnorm(830.7498, mu_Y, sd_Y, T)
    # total required stock level for 98%
    # Stock level for Germany = 8719 
    # Stock level for Switzerland = 831 
round(qnorm(.98, mu_X, sd_X) + qnorm(.98, mu_Y, sd_Y))
    
    ```
 
 
 
<br>
<br>
<br>
 
 
#### 3.	How would the stock level in Q2 change if the final localization of the SKUs happened after an order occurs? *That is, you can work with the one SKU for both countries.* How does the answer depend on the correlation of X and Y? Answer the following questions.

 1) Assume that X and Y are perfectly positively correlated.
  - What are the mean and the standard deviation for the single SKU?
  <br>
  <br>
  - Mathematical expression for the stock level of the single SKU:
  <br>
  - R code
    ```{r}
    
  # Germany (X)
mu_X <- 4200
sd_X <- 2200

# Switzerland (Y)
mu_Y <- 420
sd_Y <- 200

    # mean for the single SKU

pos_meanXY <- mu_X + mu_Y
pos_meanXY

    # std dev for the single SKU
pos_VarXY <- sd_X^2 + sd_Y^2 + 2 * sd_X * sd_Y * 1
pos_sdXY <- sqrt(pos_VarXY)
pos_sdXY
    
    # total required stock level for 98% 
positive_required <- qnorm(.98, pos_meanXY, pos_sdXY, TRUE)
positive_required
    ```
<br>

 2) Assume that X and Y are perfectly negatively correlated.
  - What are the mean and the standard deviation for the single SKU?
  <br>
  <br>
  - Mathematical expression for the stock level of the single SKU:
  <br>
  - R code
    ```{r}
    # mean for the single SKU
    
  # Germany (X)
mu_X <- 4200
sd_X <- 2200

# Switzerland (Y)
mu_Y <- 420
sd_Y <- 200
    
neg_meanXY <- mu_X + mu_Y
neg_meanXY
  
    # std dev for the single SKU
  
neg_VarXY <- sd_X^2 + sd_Y^2 + 2 * sd_X * sd_Y * (-1)
neg_sdXY <- sqrt(neg_VarXY)
neg_sdXY
  
    # total required stock level for 98% 
negative_required <- qnorm(.98, neg_meanXY, neg_sdXY, TRUE)
negative_required
    
    ```

<br>


 3) Assume that X and Y are somewhat correlated, i.e., $Corr(X,Y)=\rho$.
  - What are the mean and the standard deviation for the single SKU?
  <br>
  <br>
  - Mathematical expression for the stock level of the single SKU:
  <br>
  - R code for the stock level for $\rho \in [-1,1]$.
    ```{r}
    rho <- seq(-1, 1, 0.1)
    # mean for the single SKU

mu_X <- 4200
sd_X <- 2200

# Switzerland (Y)
mu_Y <- 420
sd_Y <- 200
    
single_MUXY <- mu_X + mu_Y  

    # std dev for the single SKU
single_VARXY <- sd_X^2 + sd_Y^2 + 2 * sd_X * sd_Y * rho
single_sdXY <- sqrt(single_VARXY)
single_sdXY

table_sd <- data.frame(rho, single_sdXY)
table_sd

    # total required stock level for 98% 
    
total_required <- qnorm(.98, single_MUXY, single_sdXY, TRUE)

table_total <- data.frame(rho, total_required)
table_total

    ```
 
<br>
<br>
